End-to-end notebook usage example

### 2024-08-09 nbs/templates/user_example/user_example.qmd

::: {#nte-installation .callout-note collapse=true title="Installing pyrovelocity"}
If you are running on a local or remote Jupyter server outside of Google Colab, we assume you have already installed pyrovelocity in the same environment in which the Jupyter kernel is running. If you have not, ensure you are in a virtual environment with python 3.10 active (we recommend [pyenv][pyenv] or [miniforge][miniforge]), and then you can install the development version from github with

>>>>

::: {#nte-installation .callout-note collapse=true title="Installing pyrovelocity"}
If you are running on a local or remote Jupyter server outside of Google Colab, we assume you have already installed pyrovelocity in the same environment in which the Jupyter kernel is running. If you have not, ensure you are in a virtual environment with python 3.11 active (we recommend [pyenv][pyenv] or [miniforge][miniforge]), and then you can install the development version from github with
